Implications of animal movement rate variation in spatial patterns of seed dispersal

### 2021-10-06 Ch1_movement_rates/Ch1_Figures.Rmd
Including ppi

load("Ch1_movement_rates/sims_backup/weib_cp.RData")
load("Ch1_movement_rates/sims_backup/weib_pp.RData")
load("Ch1_movement_rates/sims_backup/weib_np.RData")

@@

weib.boot.cp %>%
  mutate(model = "cp") %>%
  dplyr::select(., est.shape, est.scale, boot, model) %>%
  bind_rows(., weib.boot.pp %>%
              dplyr::select(., est.shape, est.scale, boot, model)) %>%
  bind_rows(., weib.boot.np %>%
              mutate(model = paste0("np_", popu)) %>%
              dplyr::select(., est.shape, est.scale, boot, model)) -> joint_weib

joint_weib %>% 
  mutate(model = factor(model, levels = c("cp", "pp", "np_1", "np_2", "np_3"))) -> joint_weib

joint_weib %>%
  group_by(model) %>%
  sample_n(., 100) %>%
  ggplot(., aes(x = model, y = est.shape)) +
  geom_violin() +
  # scale_color_manual(values = c("black", mycols)) +
  # geom_boxplot(width = 0.01) +
  # geom_point(color = "grey", alpha = 0.5) +
  # stat_summary(fun.data=mean_sdl, mult=1,
  #              geom="pointrange", color="black") +
  geom_jitter(position = position_jitter(0.1)) +
  labs(title = "Shape") +
  theme_bw() -> weib_shape

joint_weib %>%
  group_by(model) %>%
  sample_n(., 100) %>%
  ggplot(., aes(x = model, y = est.scale)) +
  geom_violin() +
  # scale_color_manual(values = c("black", mycols)) +
  # geom_boxplot(width = 0.01) +
  # geom_point(color = "grey", alpha = 0.5) +
  # stat_summary(fun.data=mean_sdl, mult=1,
  #              geom="pointrange", color="black") +
  geom_jitter(position = position_jitter(0.1)) +
  labs(title = "Scale") +
  theme_bw() -> weib_scale

>>>>

load("Ch1_movement_rates/sims_backup/weib_cp.RData")
load("Ch1_movement_rates/sims_backup/weib_pp.RData")
load("Ch1_movement_rates/sims_backup/weib_np.RData")
load("Ch1_movement_rates/sims_backup/weib_ppi.RData")

@@

weib.boot.cp %>%
  mutate(model = "cp") %>%
  dplyr::select(., est.shape, est.scale, boot, model) %>%
  bind_rows(., weib.boot.pp %>%
              dplyr::select(., est.shape, est.scale, boot, model)) %>%
  bind_rows(., weib.boot.ppi %>%
              # mutate(model = paste0(model, "_", popu)) %>% 
              dplyr::select(., est.shape, est.scale, boot, model)) %>%
  bind_rows(., weib.boot.np %>%
              mutate(model = paste0("np_", popu)) %>%
              dplyr::select(., est.shape, est.scale, boot, model)) -> joint_weib

joint_weib %>% 
  mutate(model = factor(model, levels = c("cp", "pp", "ppi", "np_1", "np_2", "np_3"))) -> joint_weib
```

```{r}
joint_weib %>%
  group_by(model) %>%
  sample_n(., 200) %>%
  ggplot(., aes(x = model, y = est.shape)) +
  geom_violin() +
  # scale_color_manual(values = c("black", mycols)) +
  # geom_boxplot(width = 0.01) +
  # geom_point(color = "grey", alpha = 0.5) +
  # stat_summary(fun.data=mean_sdl, mult=1,
  #              geom="pointrange", color="black") +
  geom_jitter(position = position_jitter(0.1)) +
  labs(title = "Shape") +
  theme_bw() -> weib_shape

joint_weib %>%
  group_by(model) %>%
  sample_n(., 200) %>%
  ggplot(., aes(x = model, y = est.scale)) +
  geom_violin() +
  # scale_color_manual(values = c("black", mycols)) +
  # geom_boxplot(width = 0.01) +
  # geom_point(color = "grey", alpha = 0.5) +
  # stat_summary(fun.data=mean_sdl, mult=1,
  #              geom="pointrange", color="black") +
  geom_jitter(position = position_jitter(0.1)) +
  labs(title = "Scale") +
  theme_bw() -> weib_scale
